VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_background.tex
re

Another disadvantage of cross-VM sharing is that it complicates 
snapshot deletion, 
which occurs frequently when snapshots expire regularly. 
The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
deletion, but still carries a significant cost, especially in the distributed cloud
setting.
%to count if a data chunk is still shared by other snapshots.

@@

In designing a VC deduplication solution, we have considered and adopted some of
the following previously-developed techniques.
\begin{itemize}
\item {\em Changed Block Tracking} --
VM snapshots can be  backed up  incrementally by identifying data segments that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
Such a scheme  is  VM-centric since deduplication is localized to the snapshot
history for each VM.
%We are seeking for a tradeoff since 
%global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
\item {\em Stateless  Data Routing} --
One approach to scalable duplicate comparison is to use a content-based hash
partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011}.
Stateless data routing divides the deduplication work with a similarity approximation. This work 
is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and 
each request is routed  to a machine which holds
a Bloom filter  or can fetch on-disk index for additional comparison.
While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
VM-specific local search.
\item {\em Sampled Index for Memory Parsimony} -- 
One effective approach that reduces memory usage is 
to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
To use a distributed memory version of the sampled index, every deduplication request
may access a remote machine for index lookup and the overall overhead of access latency for all requests
can be significant.  
\end{itemize}

>>>>

Another disadvantage of cross-VM sharing is that it complicates 
snapshot deletion, 
which occurs frequently when snapshots expire regularly. 
The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
deletion, but still carries a significant cost, especially in a distributed 
setting.
%to count if a data chunk is still shared by other snapshots.

@@

In designing a VC deduplication solution, we have considered and adopted some of
the following previously-developed techniques.
\begin{itemize}
\item {\em Changed Block Tracking} --
VM snapshots can be  backed up  incrementally by identifying data segments that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
Such a scheme  is  VM-centric since deduplication is localized to the snapshot
history for each VM.
%We are seeking for a tradeoff since 
%global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
\item {\em Stateless  Data Routing} --
One approach to scalable duplicate comparison is to use content-based hash
partitioning called stateless data routing by Dong et al.~\cite{Dong2011}.
Stateless data routing divides the deduplication work with a similarity approximation. This work 
is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and 
each request is routed  to a machine which holds
a Bloom filter  or can fetch on-disk index for additional comparison.
While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
VM-specific local search.
\item {\em Sampled Index for Memory Parsimony} -- 
One effective approach that reduces memory usage is 
to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
To use a distributed memory version of the sampled index, every deduplication request
may access a remote machine for index lookup and the overall overhead of access latency for all requests
can be significant.  
\end{itemize}

### 2014-01-31 snapshot_system/paper_dedup.tex
re

We describe our overall deduplication approach as consisting of three
complementary strategies: VM-local
duplicate search optimization, global deduplication using popular chunks, and 
VM-centric file system block management. 
%\begin{itemize}
%\item

@@

We have studied the distribution of chunk popularity~\cite{WeiZhangIEEE} 
based on a production data trace from Alibaba with over 2500 VMs.
The distribution is Zipf-like and popular chunks dominate the distribution.
We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
$\sigma$ with a range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.

Since $k$ is relatively small and these top $k$ chunks are shared among multiple VMs, 
we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.

>>>>

We describe our overall deduplication approach as consisting of three
complementary strategies: VM-local
duplicate search, global deduplication using popular chunks, and 
VM-centric file system block management. 
%\begin{itemize}
%\item

@@

We have studied the distribution of chunk popularity~\cite{WeiZhangIEEE} 
based on a production data trace from Alibaba with over 2500 VMs.
The distribution is Zipf-like and popular chunks dominate the distribution.
We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
$\sigma$ with a range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.
For example,
with top 2\% of the most popular chunks stored in PDS, up-to 40\% of the raw backup 
data can be eliminated by fingerprint lookup in PDS index.

Since $\sigma$ is relatively small and these top chunks are shared among multiple VMs, 
we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.

### 2014-01-31 snapshot_system/paper_del.tex
r
re

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/deletion.pdf, width=3in}
  \caption{Approximate deletion}
  \label{fig:deletion_flow}
\end{figure}

@@

We further propose an {\em approximate} deletion strategy to trade deletion accuracy for
speed and resource usage. Our method sacrifices a small percent of storage leakage
to efficiently identify unused chunks.
The algorithm contains three aspects.
\begin{itemize}
\item {\bf Computation for snapshot reference summary.}
Every time there is a new snapshot created,
we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
in this snapshot.
The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
For each VM we preset the vector size according to estimated VM image size;
given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
This can be done during the periodic leakage repair stage described below.

@@

\item {\bf Periodic repair of leakage}.
%[exlpain why second Bloom filter, why scan append store]
Leakage repair is conducted periodically to fix the above approximation error.
This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
A mark-and-sweep process  requires a scan of all the metadata for a snapshot store.
%Our VM-centric mark-and-sweep procedure is similar to Guo\cite{Guo2011} 
%in a way that the data dependency is clearly known.
%This generally requires a scan of almost the entire snapshot store which is much more expensive than approximate deletion,
%although certain optimized algorithms may apply\cite{Przemyslaw2013}. But 
Since it is a VM-specific procedure, 
the space cost for processing each VM is proportional to the number of chunks
within each VM. For example, the space requirement is about 85MB for a VM of size 40GB in our tested dataset.
 This is  much less expensive  than  the VM-oblivious mark-and-sweep
which scans snapshot chunks from all VMs, even with optimization~\cite{Guo2011}.

@@

%{\bf Discussion}
We now estimate the size of storage leakage and how often leak repair needs to be conducted.
Assume that  a VM keeps $h$ snapshots in the backup storage, creates and deletes one snapshot
every day. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
number of additional chunks added from one snapshot to the next snapshot version. Then the total number of 
chunks stored in a VM's snapshot store is about:
\[
U = u + (h-1)\Delta u.
\]

>>>>

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/deletion.pdf, width=2.7in}
  \caption{Fast approximate deletion}
  \label{fig:deletion_flow}
\end{figure}

@@

We further propose an {\em approximate} deletion strategy to trade deletion accuracy for
speed and resource usage. Our method sacrifices a small percent of storage leakage
to efficiently identify unused chunks.
The algorithm contains three aspects.
\begin{itemize}
\item {\bf Computation for snapshot reference summary.}
Every time there is a new snapshot created,
we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
in this snapshot.
The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
For each VM we preset the vector size according to estimated VM image size;
given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
This can be done during periodic leakage repair described below.

@@

\item {\bf Periodic repair of leakage}.
%[exlpain why second Bloom filter, why scan append store]
Leakage repair is conducted periodically to fix the above approximation error.
This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
A mark-and-sweep process  requires a scan of all the metadata for a snapshot store.
%Our VM-centric mark-and-sweep procedure is similar to Guo\cite{Guo2011} 
%in a way that the data dependency is clearly known.
%This generally requires a scan of almost the entire snapshot store which is much more expensive than approximate deletion,
%although certain optimized algorithms may apply\cite{Przemyslaw2013}. But 
Since it is a VM-specific procedure, 
the space cost is proportional to the number of chunks
within each VM. For example, the space requirement is about 85MB for a VM of size 40GB in our tested dataset.
 This is  much less expensive  than  the VM-oblivious mark-and-sweep
which scans snapshot chunks from all VMs, even with optimization~\cite{Guo2011}.

@@

%{\bf Discussion}
We now estimate the size of storage leakage and how often leak repair needs to be conducted.
Assume that  a VM keeps $h$ snapshots in the backup storage, creates and deletes one snapshot
every day. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
number of additional chunks added from one version to next snapshot version. Then the total number of 
chunks in a VM's snapshot store is about:
\[
U = u + (h-1)\Delta u.
\]

### 2014-01-31 snapshot_system/paper_intro.tex
re

In this paper we consider a backup service for converged cloud architectures
that is co-located with user VMs, sharing the cloud computer, network, and
storage resource with them.
We describe methodologies to address the following two challenges: 
1) simple deduplication and snapshot deletion with competitive efficiency and 
a small resource usage without affecting other collocated cloud services;
2) improved fault isolation for the sharing of deduplicated data,
given that node failures in converged architecture are the norm rather than
exception. 
% so that users stop incurring storage charges immediately after snapshot deletion.
%\end{itemize}

>>>>

This paper considers a backup service for converged cloud architectures
that is co-located with user VMs, sharing the cloud computer, network, and
storage resource with them.
We describe methodologies to address the following two challenges: 
1) simple deduplication and snapshot deletion with competitive efficiency and 
a small resource usage without affecting other collocated cloud services;
2) improved fault isolation for the sharing of deduplicated data,
given that node failures in converged architecture are the norm rather than
exception. 
% so that users stop incurring storage charges immediately after snapshot deletion.
%\end{itemize}
